\vspace{30mm} {\Large\bf RISC-V Duo-PLIC for the Advancced Interrupt Architecture} \\ {\large Document Version \DuoPLICRev}

### 2023-06-05 doc/src/IOMMU.tex

\textbf{%
Warning!
This chapter is only a draft, and might change significantly before
being ratified as standard by the {\RISCV} International Association.%
}
\bigskip

@@

If a naturally aligned 32-bit write is to guest physical address~$A$
within a page covered by an MRIF-mode PTE, and if the write
data is~$D$ when interpreted in the byte order indicated
by bit~2 of $A$, then the write is processed as follows:
If either $A$\z{[}11:3\z{]} or $D$\z{[}31:11\z{]} is not zero, or if
bit~2 of $A$ is one and big-endian MSIs are not supported, then the
incoming write is accepted but discarded.
Else, the original incoming write is recognized
as an MSI and is replaced by this sequence:
\begin{enumerate}

\item
In the destination MRIF, set the interrupt-pending bit for interrupt
identity $D$ to one, using either an AMOOR operation for atomic update,
or a non-atomic read-modify-write sequence.

\item
Zero-extend the \mbox{11-bit} NID value to 32~bits, and do a
\mbox{32-bit} write of this value in little-endian byte order to the
address NPPN\,\z{<<}\,12 (i.e., physical page number NPPN, page offset
zero).

\end{enumerate}
The write of step~1 must be visible to all agents in the system before
the write of step~2 becomes visible to any agent.

>>>>

\textbf{%
This chapter is \emph{frozen} and has already passed public review,
making a functional change at this stage extremely unlikely.%
}
\bigskip

@@

If a naturally aligned 32-bit write is to guest physical address~$A$
within a page covered by an MRIF-mode PTE, and if the write
data is~$D$ when interpreted in the byte order indicated
by bit~2 of $A$, then the write is processed as follows:
If either $A$\z{[}11:3\z{]} or $D$\z{[}31:11\z{]} is not zero, or if
bit~2 of $A$ is one and big-endian MSIs are not supported, then the
incoming write is accepted but discarded.
Else, the original incoming write is recognized as an MSI and is
replaced by one of the following memory accesses, setting the
interrupt-pending bit that corresponds to the interrupt identity $D$
in the destination MRIF to one:
\begin{enumerate}

\item
An atomic AMOOR operation, if the atomic updates are supported, or

\item
A non-atomic read-modify-write sequence, if non-atomic updates are supported

\end{enumerate}
Once the MRIF update operation is visible to all agents in the system,
the \mbox{11-bit} NID value is zero-extended to 32~bits, and this value
is written to the address NPPN\,\z{<<}\,12 (i.e., physical page number NPPN,
page offset zero) in little-endian byte order.
